Introducing ICBe: An Event Extraction Dataset from Narratives about International Crises

### 2023-07-13 replication_paper/psrm_draft/ICBe_manuscript.Rmd
no qmd for me

```{r umap, results='hide', echo=F, include=T, message=F, cache=F, warning=F, eval=T}
#The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.

>>>>

```{r umap, results='hide', echo=F, include=T, message=F, cache=F, warning=F, eval=F}
#The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.
